\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2018-06-13 write_up/mixfishsim_ecolmod.tex
Updated overview figure for manuscript

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Overview schematic  
\begin{figure}[!ht]
	\hspace{-4em}
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going below,    % General flow is top-to-bottom
    node distance=8mm and 60mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    scale=0.9,
    every node/.style={scale=0.8}]                 
    \label{fig:model}
    % ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
  proc/.style={base, rectangle, text width=8em},
  test/.style={base, rectangle, text width=5em},
  term/.style={proc, rounded corners},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes in the middle
\node [proc, densely dotted, it] (p0) {start};
% Use join to connect a node to the previous one 
\node [term, join, fill=lcnorm!25]      {Choose random location to fish};
\node [term, join, fill=lcfree!25] (p1){Sample catch};
\node [test, densely dotted] (t1) {if $spawn_{t}$};
\node [test, join, densely dotted] (t2) {if $wk_{t}$ != $wk_{t-1}$};
\node [test, join, densely dotted] (wk) {if $day_{t}$ != $day_{t-1}$};
\node [test, join, densely dotted] (t3) {if $trip_{t}$ != $trip_{t-1}$};
\node [term, join, fill=lcnorm!25]  (p2) {Correlated Random Walk};
\node [term, join, fill=lcnorm!25]  (p3) {Choose new fishing location};
\node [proc, densely dotted, join, it] (p7) {end};

@@

% -------------------------------------------------
% A couple of boxes have annotations
\node [below=of p0, it, yshift=1.5em,xshift=-3em] {$t==1$};
\node [right=30mm of p3, it] {$1 < t < t_{max}$};
\node [below=of p3, it,xshift=-3em, yshift=1.5em] {$t == t_{max}$};

@@

% -------------------------------------------------
% A last flourish which breaks all the rules
\draw [->,purple, dotted, thick, shorten >=1mm]
  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
  |- node [black, near end, yshift=1.75em, it]
    {} ($(p1.north) + (0,0.3)$);
% -------------------------------------------------
\end{tikzpicture}
\caption{Overview Schematic of simulation model. The blue boxes indicate fleet
	dynamics processes, the green boxes population dynamics processes while
	the white boxes are the timesteps at which processes occur; $t$ = tow,
	$tmax$ is the total number of tows, $wk$ is a weekly timestep, $day$ is
	a day timestep, $trip$ is a trip time step. \textcolor{red}{I NEED TO
		REDO THIS TO MAKE NOTATION MORE CONCISE AND CONSISTENT} } 
\label{fig:overview}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
confirmed past activity and past catch rates are strong predictors of fishing
location choice. For this reason, the fleet dynamics sub-model
include\replaced[id=PD]{d}{s} a learning component, where a vessel's initial
fishing location in a trip \replaced[id=PD]{wa}{i}s based on selecting from
previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
by sorting all previous fishing events in the previous trip as well as the
previous time periods in past years, and choosing randomly from the top 75 \%
of fishing events \replaced[id=PD]{as defined by the revenue gained}{in value}.
Simulation testing indicated that this learning increased the mean value of
catches for the vessels, over just relying on the correlated random
walk \todo{\added[id=JJ]{Correlated random walk of what}} function
\added[id=PD]{as described for the 'within trip' decisions below}.

@@

Fishing locations within a trip are determined by a modified random walk
process. A random walk type was chosen as it is the simplest assumption
commonly used in ecology to describe \added[id=PD]{optimal} animal
\deleted[id=PD]{movement which} search\replaced[id=PD]{ strategy}{ing} for
\added[id=PD]{exploiting} homogeneously distributed prey about which there is
uncertain knowledge \citep{Viswanathan1999}. In a random walk, movement is a
stochastic process through a series of steps\added[id=JJ]{. These steps have a
	length, and a direction} that can either be equal in length or take
some other functional form. The direction of the random walk can be correlated,
a characteristic known as `persistence', providing some overall
\deleted[id=PD]{location of} directional movement \citep{Codling2008}
\deleted[id=PD]{or uncorrelated}. \\

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Overview schematic  
\begin{figure}[!ht]
	\hspace{-4em}
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going below,    % General flow is top-to-bottom
    node distance=8mm and 60mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    scale=0.9,
    every node/.style={scale=0.8}]                 
    \label{fig:model}
    % ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
  proc/.style={base, rectangle, text width=8em},
  test/.style={base, rectangle, text width=5em},
  term/.style={proc, rounded corners},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes in the middle
\node [proc, densely dotted, it] (p0) {start};
% Use join to connect a node to the previous one 
\node [term, join, fill=lcnorm!25]      {Choose random location to fish};
\node [term, join, fill=lcfree!25] (p1){Sample catch};
\node [test, densely dotted] (t1) {if $Rec_{p}[t]$};
\node [test, join, densely dotted] (t2) {if $wk[t] \neq  wk[t-1]$};
\node [test, join, densely dotted] (wk) {if $day[t] \neq day[t-1]$};
\node [test, join, densely dotted] (t3) {if $trip[t] \neq trip[t-1] \ | \ PK[t]$};
\node [term, join, fill=lcnorm!25]  (p2) {Correlated Random Walk};
\node [term, join, fill=lcnorm!25]  (p3) {Choose new fishing location};
\node [proc, densely dotted, join, it] (p7) {end};

@@

% -------------------------------------------------
% A couple of boxes have annotations
\node [below=of p0, it, yshift=1.5em,xshift=-3em] {$t=1$};
\node [right=30mm of p3, it] {$1 < t < t_{max}$};
\node [below=of p3, it,xshift=-3em, yshift=1.5em] {$t = t_{max}$};

@@

% -------------------------------------------------
% A last flourish which breaks all the rules
\draw [->,purple, dotted, thick, shorten >=1mm]
  (p3.south) -- ++(5mm,-3mm)  -- ++(87mm,0mm) 
  |- node [black, near end, yshift=1.75em, it]
    {} ($(p1.north) + (0,0.3)$);
% -------------------------------------------------
\end{tikzpicture}
\caption{Overview Schematic of simulation model. The blue boxes indicate fleet
	dynamics processes, the green boxes population dynamics processes while
	the white boxes are the timesteps at which processes occur; $Rec$
	is a recruitment period for population $p$, $t$ = tow, $tmax$ is the
	total number of tows, $wk$ is a weekly timestep, $day$ is a day
	timestep, $trip$ is a trip time step.}
\label{fig:overview}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
confirmed past activity and past catch rates are strong predictors of fishing
location choice. For this reason, the fleet dynamics sub-model
include\replaced[id=PD]{d}{s} a learning component, where a vessel's initial
fishing location in a trip \replaced[id=PD]{wa}{i}s based on selecting from
previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
by \added[id=PD]{calculating expected profit from locations fished during}
previous fishing events in the previous trip as well as the previous time
periods in past years, and choosing randomly from the top 75 \% of fishing
events \replaced[id=PD]{as defined by the expected profit}{in value}.
\added[id=PD]{Expected profit was estimated from the revenue from previous
	times fished at a location minus the fuel cost of travelling to the
	location.} Simulation testing indicated that this learning increased
the mean value of catches for the vessels, over just relying on the correlated
random walk \todo{\added[id=JJ]{Correlated random walk of what}} function
\added[id=PD]{as described for the 'within trip' decisions below}.

@@

Fishing locations within a trip are \added[id=PD]{initially} determined by a
modified random walk process. \added[id=PD]{As the simulation progresses, the
	within-trip decision become gradually more influenced by past locations
	fished, based on the same process as the initial location, influenced
	by expected profit at a fishing location.} A random walk was chosen for
the exploratory fishing process as it is the simplest assumption commonly used
in ecology to describe \added[id=PD]{optimal} animal \deleted[id=PD]{movement
	which} search\replaced[id=PD]{ strategy}{ing} for
\added[id=PD]{exploiting} homogeneously distributed prey about which there is
uncertain knowledge \citep{Viswanathan1999}. In a random walk, movement is a
stochastic process through a series of steps\added[id=JJ]{. These steps have a
	length, and a direction} that can either be equal in length or take
some other functional form. The direction of the random walk can be correlated,
(known as `persistence'), providing some overall \deleted[id=PD]{location of}
directional movement \citep{Codling2008} \deleted[id=PD]{or uncorrelated}. \\
